\chapter{Introduction}

Augmented reality (AR) technologies have revolutionized various industries, offering innovative solutions to complex problems. Quality control systems are one such area where AR can provide immense value. While similar applications exist on platforms like the iPad, their limitations in spatial capabilities and less intuitive interaction methods make them less suitable for high-precision tasks. In this project, we have developed a quality control system tailored for the Apple Vision Pro (AVP), leveraging its advanced spatial capabilities, immersive experience, and intuitive gesture-based controls.

Having completed the core functionality in the first phase—including inspection workflows, basic positioning, and automated report generation—this second phase of our project shifts focus to advancing object tracking and introducing custom annotation features. These enhancements aim to make the system more dynamic and adaptable, harnessing the Vision Pro’s superior sensor and processing capabilities. By leveraging this more powerful hardware, we expect to achieve greater tracking precision and provide a richer, more intuitive user experience for industrial quality control applications.

\section{Project Definition}

The aim of this project is to develop a quality control system specifically designed for the Apple Vision Pro (AVP). Unlike iPads, which have limited spatial features, the AVP offers advanced spatial capabilities and immersive interaction methods that make it ideal for high-precision tasks. This system leverages the AVP’s strengths to improve accuracy and efficiency in quality control processes.

The key functionalities include aligning 3D CAD models with real-world objects, enabling interactive inspections at both predefined and custom annotation points, supporting dynamic (user-defined) annotations, implementing real-time object tracking (not just initial positioning), and generating detailed quality analysis reports. Unlike tablet-based systems—which often suffer from limited depth perception, reduced tracking stability, and less natural interaction methods—our solution leverages Vision Pro’s advanced hardware to overcome these barriers. By providing enhanced spatial understanding, intuitive gesture and gaze-based controls, and robust tracking, this project offers a precise, efficient, and user-friendly platform for industrial quality control applications.


% This project focuses on designing and implementing a quality control system for the Apple Vision Pro (AVP). The system utilizes the AVP's cutting-edge spatial and interaction capabilities to enhance accuracy and user experience. The core functionality revolves around:
% \begin{itemize}
%     \item Aligning 3D CAD models with real-world objects to identify differences.
%     \item Providing users with tools for interactive and natural inspection using gesture-based controls.
%     \item Generating quality analysis reports in Excel format for documentation and review.
%     \item Allowing users to inspect predefined points on models for detailed quality control.
% \end{itemize}

% During the inspection process, users can select specific inspection points on the model to perform quality checks. These inspections can include:
% \begin{itemize}
%     \item Yes/No Verification: Confirming whether a feature meets the required specifications.
%     \item Description-based Analysis: Providing detailed notes about the inspected feature.
%     \item Count-based Evaluation: Counting the number of specific elements.
% \end{itemize}

% The application is designed to support industries where precise quality control is critical, such as manufacturing, automotive, and aerospace.

\section{Project Aims}

The primary aims of the second phase of this project are as follows:
\begin{enumerate}
    \item \textbf{Enhanced User Experience:} Refine and optimize the UI/UX for even more intuitive, gesture-driven interaction, leveraging advanced features like gaze tracking and improved finger gesture recognition.
    \item \textbf{Precise Object Tracking:} Move beyond initial alignment to implement robust, real-time tracking of objects in the environment, enabling consistent spatial registration and minimizing drift during use.
    \item \textbf{Custom Annotations:} Enable users to create, place, and edit dynamic, user-defined annotation points directly in AR, rather than being limited to only predefined inspection locations.
    \item \textbf{Advanced Reporting:} Extend the reporting functionality to include annotation data, allowing users to generate comprehensive quality control reports that reflect both inspection results and user-added insights.
    \item \textbf{Performance Improvements:} Further optimize system performance to ensure smooth, low-latency operation—even with the added complexity of dynamic annotations and continuous tracking.
\end{enumerate}

These enhancements build directly upon the foundation established in the first phase, aiming to deliver a more dynamic, precise, and adaptable quality control solution powered by the Apple Vision Pro.